Ride at Your Own Risk: Insights into Toronto’s Bicycle Theft Hotspots

### 2024-11-12 paper/paper.Rmd
title, subtitle, description formatted

.title {
  font-size: 70px;            /* Larger font size for the main title */
  font-weight: bold;          /* Bold font weight for emphasis */
  color: #FFC107;             /* Yellow color similar to the example */
  text-align: left;           /* Align text to the left */
  font-family: Georgia, serif; /* Use Georgia or a similar serif font */
  margin: 0;
  line-height: 1.1;           /* Tighter line height */
}

.subtitle {
  font-size: 40px;            /* Slightly larger font size for the subtitle */
  font-weight: normal;        /* Normal font weight */
  color: white;               /* White color for the subtitle */
  text-align: left;           /* Align text to the left */
  font-family: 'Times New Roman', Times, serif; /* A serif font for contrast */
  margin-top: 10px;
  line-height: 1.2;           /* Adjust line height for spacing */
}

.description {
  display: block; /* Makes span act like a block element */
  font-size: 20px;
  font-weight: normal;
  font-style: italic; /* Makes the text italic */
  line-height: 1.6;
  text-align: left;
  max-width: 600px;
  margin-top: 20px;
  font-family: "Times New Roman", Times, serif; /* Change to desired font */
  background-color: transparent !important;
  border: none !important;
  padding: 0 !important;
  box-shadow: none !important;
}

.author-date {
  font-size: 18px;
  font-weight: normal;
  color: white;
  text-align: left;
  margin-top: 30px;
  font-style: italic;
}

>>>>

.title {
  font-size: 70px;                   /* Larger font size for the main title */
  font-weight: bold;                 /* Bold font weight for emphasis */
  color: #FFC107;                    /* Yellow color similar to the example */
  text-align: left;                  /* Align text to the left */
  font-family: Georgia, serif;       /* Use Georgia or a similar serif font */
  margin: 0;
  line-height: 1.1;                  /* Tighter line height */
  padding: 10px;                     /* Add padding around text */
  border: 5px solid #FFC107;         /* Border around the title text */
  border-radius: 8px;                /* Rounded corners for a softer look */
  display: inline-block;             /* Keeps the border tight around text */
  text-shadow: 3px 3px 8px rgba(0, 0, 0, 0.7); /* Text shadow for emphasis */
  box-shadow: 0px 4px 10px rgba(0, 0, 0, 0.5); /* Optional shadow for depth */
}

.subtitle {
  font-size: 40px;            /* Slightly larger font size for the subtitle */
  font-weight: normal;        /* Normal font weight */
  color: white;               /* White color for the subtitle */
  text-align: left;           /* Align text to the left */
  font-family: 'Times New Roman', Times, serif; /* A serif font for contrast */
  margin-top: 10px;
  line-height: 1.2;           /* Adjust line height for spacing */
  text-shadow: 3px 3px 8px rgba(0, 0, 0, 0.7); /* Text shadow for emphasis */
}

.description {
  display: block; /* Makes span act like a block element */
  font-size: 20px;
  font-weight: normal;
  font-style: italic; /* Makes the text italic */
  line-height: 1.6;
  text-align: left;
  max-width: 600px;
  margin-top: 20px;
  font-family: "Times New Roman", Times, serif; /* Change to desired font */
  background-color: transparent !important;
  border: none !important;
  padding: 0 !important;
  box-shadow: none !important;
  text-shadow: 3px 3px 8px rgba(0, 0, 0, 0.7); /* Text shadow for emphasis */
}

.author-date {
  font-size: 18px;
  font-weight: normal;
  color: white;
  text-align: left;
  margin-top: 30px;
  font-style: italic;
  text-shadow: 3px 3px 8px rgba(0, 0, 0, 0.7); /* Text shadow for emphasis */
}
